Gaia's constraints on the very massive (initially $\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-25 VFTS682_APJL.tex
sec. discussion edited

\begin{figure*}[htbp]
  \centering
  \includegraphics[width=0.35\textwidth]{figures/dist_mu_region.pdf}
  \includegraphics[width=0.35\textwidth]{figures/angle}
  \caption{\emph{Left panel}: distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136. VFTS682 is not an outlier, but
    its relative proper motion matches the expected value if it were indeed
    ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. The top axis shows the conversion to physical units
    assuming a distance of 50\,kpc. \emph{Right panel}:  distribution of
    angles between the relative proper motion direction and the radial
    direction from the center of the cluster to the star. The error bars from \emph{Gaia} for VFTS682 are large, but
    the best value is in agreement with the hypothesis of dynamical
    ejection. In both
    panels, the dark blue histograms contain 317 
    stars with error smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
    lighter blue histograms contain 36 stars with errors smaller than $0.05\,\mathrm{mas \
      yr^{-1}}$.\todo{possibly: cartoon to illustrate angle definition, or add to
    fig.2 if not too messy, maybe also show HST measurements on this
    plot for 682? Redo right panel taking care of projection of the
    radial directions!It's misleading!}}
  \label{fig:dist}
\end{figure*}

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.48\textwidth]{./figures/main_plot_good_gaia_only}  
  \caption{\SdM{I don't see a reason why we would not show the HST data, except for wanting to hide it maybe.  Let's sit together and find a good way to plot both.  (Hope you still have the script to show the HST direction. )}  The red solid arrow indicates the proper motion of VFTS682 
    relative to the region from \emph{Gaia} DR2, starting from the present day position of
    the star. The yellow arrows indicate the possible
    directions of projected motion within the \emph{Gaia} DR2 errors, and are extended
    backwards (dashed) to illustrate the uncertainty on the origin of the
    star. The length of the prolongations is proportional to the relative proper motion
    times the age of VFTS682 \citep[$1.0\pm0.2$\,Myr,][]{schneider:18}.
    % \todo{load color picture on background? Fig with HST data
    % available, but confusing...}
  }

>>>>

\begin{figure*}[htbp]
  \centering
  \includegraphics[width=0.35\textwidth]{figures/dist_mu_region.pdf}
  \includegraphics[width=0.35\textwidth]{figures/angle}
  \caption{\emph{Left panel}: distribution of OB-type and Wolf-Rayet stars in proper
    motion relative to R136. VFTS682 is not an outlier, but
    its relative proper motion matches the expected value if it were indeed
    ejected from R136 assuming an age of $1.0\pm0.2$\,Myr. The top axis shows the conversion to physical units
    assuming a distance of 50\,kpc. \emph{Right panel}:  distribution of
    angles between the relative proper motion direction and the radial
    direction from the center of the cluster to the star. The error bars from \emph{Gaia} for VFTS682 are large, but
    the best value is in agreement with the hypothesis of dynamical
    ejection. In both
    panels, the dark blue histograms contain 317 
    stars with error smaller than $0.1\,\mathrm{mas \
      yr^{-1}}\simeq25\,\mathrm{km\ s^{-1}}$ at 50\,kpc, the
    lighter blue histograms contain 36 stars with errors smaller than $0.05\,\mathrm{mas \
      yr^{-1}}$.}
  \label{fig:dist}
\end{figure*}

@@

\begin{figure}%[tbp]
  \centering
  \includegraphics[width=0.48\textwidth]{./figures/main_plot_good_gaia_only}  
  \caption{The red solid arrow indicates the proper motion of VFTS682 
    relative to the region from \emph{Gaia} DR2, starting from the present day position of
    the star. The yellow arrows indicate the possible
    directions of projected motion within the \emph{Gaia} DR2 errors, and are extended
    backwards (dashed) to illustrate the uncertainty on the origin of the
    star. The length of the prolongations is proportional to the relative proper motion
    times the age of VFTS682 \citep[$1.0\pm0.2$\,Myr,][]{schneider:18}.
    % \todo{load color picture on background? Fig with HST data
    % available, but confusing...}
  }
